---
title: "Lab 03 - Nobel laureates"
author: "Hannah, Andrew, Kristen, Zety"
date: "`r Sys.Date()`"
output: html_document
---


### Load packages and data

```{r load-data, message = FALSE, warning=FALSE}
library(tidyverse) 
```


```{r reading-nobel-data , message = FALSE}

nobel <- read_csv("data/nobel.csv")
```

### Exercise 1

#### Narrative

There are 935 observations with 26 variables in the data set.
Each row represents the different the different award winners.


### Exercise 2

#### Code

```{r nobel-living}
# remove this comment and add your code here
```

#### Narrative

*Remove this text and add your answer here.*


### Exercise 3

#### Code

```{r facet-bar-plot}
# remove this comment and add your code here
```

#### Narrative

*Remove this text and add your answer here.*


### Exercise 4

#### Code

```{r born-country-us}
# remove this comment and add your code here
```


### Exercise 5

#### Narrative

*Remove this text and add your answer here.*

#### Code

```{r facet-bar-plot-redo}
# remove this comment and add your code here
```


### Exercise 6

#### Code

```{r born-country}
# remove this comment and add your code here
```

#### Narrative

*Remove this text and add your answer here.*